When environmentally persistent pathogens transform good habitat into ecological traps

### 2015-07-09 Manuscript/manuscript.tex
Redo figure 1 and longevity labels

\begin{figure}
\includegraphics[scale=0.5]{figure/figure_1.pdf}
\caption{The proportion of simulations resulting in endemic disease dynamics (persistence of both susceptible and infectious hosts) as a function of infectious survival ($\nu$), and the probability of direct transmission ($\delta$).  Panel columns show low (0.3, a, d), medium (1.0, b, e), and high (3.2, c, f) pathogen longevities, while rows show low quality (ranging from 0.23 to 1.24, a - c) and high quality (ranging from 0.76 to 1.77, d - f) patch quality distributions.  Darker shading corresponds to more frequent endemic dynamics.  The white region above the endemic region generally corresponds to pandemic dynamics (no susceptible host populations persist), while the region below the endemic region corresponds to disease-free dynamics. PCC: in this figure and in Fig 2 I'd put write the longevities in each sub-figure and remove the longevity label from the x-axis. I'd prefer to not refer to the persistence of susceptible patches as a "endemic". Maybe this figure should instead be a heatmap of the percentage of patches infected. This can then be contrasted with Fig.2 showing that only in the intermediate infection scenarios are there traps. This avoids the "endemic" v. pandemic issue}
\label{endemic}
\end{figure}

\begin{figure}
\includegraphics[scale=0.5]{figure/figure_2.pdf}
\centering
\caption{Differences between the median total effective population size of hosts on low quality patch distributions (quality between 0.23 to 1.24) and high quality patch distributions (quality between 0.76 and 1.77) as a function of disease-induced mortality ($\nu$) and the probability of direct transmission ($\delta$).  Reds indicate that high quality habitat distributions support higher median host population sizes than low quality habitat, primarily corresponding to pathogens with either very limited or very extensive spread. Conversely, blues indicate higher median host population sizes on low quality habitat distributions, corresponding to pathogens with intermediate levels of spread.  Panel columns show low (0.3, a), medium (1.0, b), and high (3.2, c) pathogen longevities.}
\label{highvlow}
\end{figure}

\begin{figure}
\includegraphics[scale=0.5]{figure/figure_3.pdf}
\centering
\caption{Boxplots showing the range, over 100 replicate simulations, of susceptible (a), infectious (b), and total (c) host population sizes for high quality (red) and low quality (blue) habitat distributions.  Disease-induced mortality ($\nu$) and direct transmission rate ($\delta$) are fixed at values of 0.2 and 0.3, respectively.  Colored points show medians, while vertical lines indicate the inner-quartile ranges, with horizontal lines indicating the minimum and maximum.  At low longevities, this pathogen is largely unable to invade and high quality habitat supports larger populations of susceptible hosts.  However, low quality habitat is better able to maintain these susceptible hosts as the pathogen's longevity increases, leading to larger total population sizes. PCC: seems like you chose different longevities here for your low,med, high scenarios than in Fig. 1&2. Not a big issue, but might point out that the low longevity here is really just a no-disease, completely healthy scenario}
\label{popsizes}
\end{figure}

>>>>

\begin{figure}
\includegraphics[scale=0.5]{figure/figure_1.pdf}
\caption{Median total susceptible population size as a function of infectious survival ($\nu$), and the probability of direct transmission ($\delta$).  Panel columns show low (0.3, a, d), medium (1.0, b, e), and high (3.2, c, f) pathogen longevities, while rows show low quality (ranging from 0.23 to 1.24, a - c) and high quality (ranging from 0.76 to 1.77, d - f) patch quality distributions.  Darker shading corresponds to larger population sizes.}
\label{endemic}
\end{figure}

\begin{figure}
\includegraphics[scale=0.5]{figure/figure_2.pdf}
\centering
\caption{Differences between the median total effective population size of hosts on low quality patch distributions (quality between 0.23 to 1.24) and high quality patch distributions (quality between 0.76 and 1.77) as a function of infectious survival ($\nu$) and the probability of direct transmission ($\delta$).  Reds indicate that high quality habitat distributions support higher median host population sizes than low quality habitat, primarily corresponding to pathogens with either very limited or very extensive spread. Conversely, blues indicate higher median host population sizes on low quality habitat distributions, corresponding to pathogens with intermediate levels of spread.  Panel columns show low (0.3, a), medium (1.0, b), and high (3.2, c) pathogen longevities.}
\label{highvlow}
\end{figure}

\begin{figure}
\includegraphics[scale=0.5]{figure/figure_3.pdf}
\centering
\caption{Boxplots showing the range, over 100 replicate simulations, of susceptible (a), infectious (b), and total (c) host population sizes for high quality (red) and low quality (blue) habitat distributions.  Disease-induced mortality ($\nu$) and direct transmission rate ($\delta$) are fixed at values of 0.2 and 0.3, respectively.  Colored points show medians, while vertical lines indicate the inner-quartile ranges, with horizontal lines indicating the minimum and maximum.  At low longevities, this pathogen is unable to invade and high quality habitat supports larger populations of susceptible hosts.  However, low quality habitat is better able to maintain these susceptible hosts as the pathogen's longevity increases, leading to larger total population sizes.}
\label{popsizes}
\end{figure}
